---
output: github_document
always_allow_html: true
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE,
  warning = FALSE,
  fig.retina = 2,
  fig.align = 'center'
)

library(desc)
library(dplyr)
library(readr)
library(gt)
library(kableExtra)
library(fontawesome)

package <- desc::desc_get_field("Package")
organisation <- desc::desc_get_field("Organisation") # Assuming you have an 'Organisation' field in DESCRIPTION
organisation_package <- paste0(organisation, "/", package)
browser_favicon_colour <- "lightblue"

# Conditionally install and load the package
if (!requireNamespace(package, quietly = TRUE)) {
  devtools::install_github(organisation_package, dependencies = TRUE, upgrade = "never")
}
library(package, character.only = TRUE)

# Assuming main dataset is also named after the package
data(list = package, package = package)

```

# `r desc::desc_get_field("Package")`
***`r desc::desc_get_field("Title")`***

<!-- badges: start -->

[![License: CC BY
4.0](https://img.shields.io/badge/License-CC_BY_4.0-lightgrey.svg)](https://creativecommons.org/licenses/by/4.0/)

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.15423460.svg)](https://zenodo.org/doi/10.5281/zenodo.15423460)

<!-- badges: end -->

`r desc::desc_get_field("Description")`

-----

## Installation

You can install the development version of ``r desc::desc_get_field("Package")`` from GitHub `r fontawesome::fa("github")` with:

``` r
devtools::install_github(`r organisation_package`, dependencies = TRUE)
```

-----

### Download as CSV Files

If you prefer to work with the data outside of R, you can download individual datasets as CSV files.

1.  **Right-click** on the "Download CSV" link for the dataset you want.
2.  Select **"Save Link As"**  [`r fontawesome::fa("chrome", fill = browser_favicon_colour)`](https://www.google.com/chrome/) [`r fontawesome::fa("edge", fill = browser_favicon_colour)`](https://www.microsoft.com/edge/) [`r fontawesome::fa("firefox", fill = browser_favicon_colour)`](https://www.mozilla.org/firefox/) or **"Download Linked File"** [`r fontawesome::fa("safari", fill = browser_favicon_colour)`](https://www.apple.com/safari/).
3.  Choose where you'd like to save the file on your computer.

</center>\n 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
extdata_path <- c(paste0(desc::desc_get_field("URL"), "/raw/main/inst/extdata/"))

readr::read_csv("data-raw/dictionary.csv") |>
  dplyr::distinct(file_name) |>
  dplyr::mutate(file_name = stringr::str_remove(file_name, ".rda")) |>
  dplyr::rename(dataset = file_name) |>
  dplyr::mutate(
    CSV = paste0("[Download CSV](", extdata_path, dataset, ".csv)")
  ) |>
  knitr::kable()

```

 \n</center>\n 
 
## Data
``` r
library(`r package`)
```

### glaas

The dataset ``r desc::desc_get_field("Package")`` has `r nrow(get(desc::desc_get_field("Package")))` observations and `r ncol(get(desc::desc_get_field("Package")))` variables

``` r
get(`r package`) |> 
  head(3) |> 
  gt::gt() |>
  gt::as_raw_html()
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
get(package) |> 
  head(3) |> 
  gt::gt() |>
  gt::as_raw_html()
```

-----

For an overview of the variable names, see the following table.

```{r echo=FALSE, message=FALSE, warning=FALSE}
readr::read_csv("data-raw/dictionary.csv") |>
  dplyr::filter(file_name == paste0(package, ".rda")) |>
  dplyr::select(variable_name:description) |> 
  knitr::kable(booktabs = TRUE) |> 
  kableExtra::kable_styling(
    full_width = FALSE,
    bootstrap_options = c("striped"),
    position = "center"
  )
```

## License

Data are available as
[CC-BY](https://github.com/openwashdata/`r package`/blob/main/LICENSE.md).

## Citation

```{r, echo=FALSE, message=FALSE, warning=FALSE}
citation(package)
```
