---
title: "Get Started with glaas"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started with glaas}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installation

You can install `glaas` from GitHub:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("openwashdata/glaas")
```

## Loading the data

```{r}
library(glaas)
```

Thanks to lazy loading, the dataset is available directly after loading the package - no need to call `data("glaas")`.

### A note on lazy loading

This package uses **lazy loading**, which means the dataset isn't loaded into memory until you actually use it. This keeps the package lightweight when you first load it.

Here's an example to illustrate the concept:

```r
lobstr::mem_used()
#> 48.74 MB

library(glaas)
lobstr::mem_used()
#> 50.54 MB

invisible(glaas)
lobstr::mem_used()
#> 91.24 MB
```

Notice how loading the package only adds ~2 MB to memory. The full dataset (~40 MB) is only loaded when you actually reference it.

## Overview

The `glaas` dataset contains data from the UN-Water Global Analysis and Assessment of Sanitation and Drinking-water (GLAAS) survey. It includes **`r nrow(glaas)` rows** and **`r ncol(glaas)` variables** covering multiple survey cycles.

```{r}
# Survey cycles available
unique(glaas$time_period)

# Number of countries
length(unique(glaas$country_name))
```

## Exploring the data

```{r}
# Preview the dataset
head(glaas)

# Check available thematic areas
unique(glaas$grand_parent_text)
```

For a complete description of all variables, see `?glaas`.
